My title

### 2024-02-19 paper/paper.qmd
Committing changes made to analysis_data_csv, paper.qmd, and data_cleaning.R up until this point (Feb 18 @ 9:34pm).

library(ggplot2) # used to create figure
library(gridExtra) # used to print figure
library(dplyr) # for data manipulation
library(broom) # for tidy function
library(readr) # for read_csv
library(stringr) # for string manipulation
library(purrr)
library(patchwork)
library(tidyr)
library(gridExtra)
library(magrittr)
library(stats)
library(kableExtra)
library(ggplot2)
library(broom)
library(modelsummary)
library(here)
library(stargazer)
library(gt)
library(readr)
library(dplyr)
library(rstanarm)

@@

This paper aims to replicate the study conducted by Raychaudhuri, Mendelberg, and McDonough, focusing on their original research question: "Is sympathy for drug users racially selective among White Americans?" However, it will extend the inquiry by examining the role of political ideology in shaping White Americans' reactions to sympathetic media portrayals of opioid abuse. Specifically, it will investigate whether political ideology conditions the extent of racial selectivity in empathetic responses to drug users.

@@

### Methodology
This paper will replicate the survey data that was originally collected for the (2022) paper by Raychaudhuri, Mendelberg, and McDonough. The study constructed a hypothetical newspaper story about opioid abuse, varying the race of the users (Black or White) and the valence of the frame (sympathetic or unsympathetic). The focus on Black and White racialized groups was guided by the White “face” of the opioid epidemic in contrast to the Black “face” of other drug epidemics @Raychaudhuri2022. The authors then conducted two randomized between-subjects survey experiments on two separate samples. The main sample consists of 1,517 White American adults from the NORC Amerispeak Panel, a national probability based sample. The other sample was from the survey firm Dynata. The authors discribe the process as follows: "Each participant was randomly assigned to one of four treatments or a no-story control. In the treatments, respondents read a hypothetical news story about drug use, varying the race of users (White or Black) and the valence of the frame (sympathetic or unsympathetic)" @Raychaudhuri2022.

@@

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"), show_col_types = FALSE)

data_long <- analysis_data |>
  select(sympathetic_white, sympathetic_black, unsympathetic_white, unsympathetic_black, policy) |>
  pivot_longer(cols = -policy, names_to = "category", values_to = "value") |>
  filter(value == 1) |>
  group_by(category) |>
  summarise(support_for_treatment = mean(policy, na.rm = TRUE),
            support_for_arrest = 1 - support_for_treatment)

data_long_melted <- pivot_longer(data_long, cols = c(support_for_treatment, support_for_arrest),
                                 names_to = "policy_type", values_to = "proportion") |>
  mutate(policy_type = factor(policy_type, levels = c("support_for_treatment", "support_for_arrest")))

ggplot(data_long_melted, aes(x = category, y = proportion, fill = policy_type)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = c("support_for_treatment" = "blue", "support_for_arrest" = "red")) +
  labs(title = "Policy Support by Valence and Race (Media Frames)",
       x = "Valence and Race",
       y = "Proportion",
       fill = "Policy Type") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

# Create the Forest Plot
ggplot(tidy_model, aes(x = estimate, y = term)) +
  geom_point() + # Add points for estimates
  geom_errorbarh(aes(xmin = estimate - std.error, xmax = estimate + std.error), height = 0.2) + # Error bars
  theme_minimal() + # Use a minimal theme
  labs(x = "Estimate", y = "Variable", title = "Forest Plot of Ideology Model Estimates") + # Labels
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") # Vertical line at zero
```

@@

The null hypothesis ($H_0$) stated that there would be no interaction effect between political ideology and media framing on support for opioid abuse treatment policy. However, @fig-interactions shows varying estimates across different combinations of political ideology and media framing. This suggests that there may be an interaction effect. This is because the estimates for both liberal and conservative ideologies when paired with certain sympathetic framings are positive and do not overlap with the zero line, indicating a significant effect. This suggests that there is indeed some interaction effect, which leads to the rejection of the null hypothesis.

@@

# Future Research 
Future research could look into the psychological mechanisms that may explain why and how political ideologies modulate responses to media framing of opioid users. It is also imperative to understand the role of individual identity, such as race and personal experience with opioid abuse, in shaping one's reaction to policy framing. Could it be that personal connections to the opioid crisis, either through community impact or personal acquaintance with sufferers, are powerful enough to override political predispositions? Personal experience could play a significant role in an individuals views on media framing and policy and seems like a strong future area of research reagrding both this paper and the original.

# Conclusion 
This study contributes to the growing body of literature that seeks to understand the opioid crisis not just as a public health issue, but as a societal issue that is deeply intertwined with race, politics, and media. By replicating and extending the work of Raychaudhuri, Mendelberg, and McDonough, this paper sheds light on the nuanced ways in which these factors interact to shape policy preferences, offering insights that could inform more effective and equitable approaches to addressing the opioid epidemic.

>>>>

@@

This paper aims to replicate the study conducted by Raychaudhuri, Mendelberg, and McDonough, focusing on their original research question: "Is sympathy for drug users racially selective among White Americans?" However, it will extend the inquiry by examining the role of political ideology in shaping White Americans' reactions to sympathetic media portrayals of opioid abuse. Specifically, it will investigate whether political ideology conditions the extent of racial selectivity in empathetic responses to drug users. The paper will reveal that there is some level of there is indeed some interaction effect between media frames and the ideological spectrum on support for treatment related policy.

@@

### Methodology
This paper will replicate the survey data that was originally collected for the (2022) paper by Raychaudhuri, Mendelberg, and McDonough. The study constructed a hypothetical newspaper story about opioid abuse, varying the race of the users (Black or White) and the valence of the frame (sympathetic or unsympathetic). The focus on Black and White radicalized groups was guided by the White “face” of the opioid epidemic in contrast to the Black “face” of other drug epidemics @Raychaudhuri2022. The authors then conducted two randomized between-subjects survey experiments on two separate samples. The main sample consists of 1,517 White American adults from the NORC Amerispeak Panel, a national probability based sample. The other sample was from the survey firm Dynata. The authors describe the process as follows: "Each participant was randomly assigned to one of four treatments or a no-story control. In the treatments, respondents read a hypothetical news story about drug use, varying the race of users (White or Black) and the valence of the frame (sympathetic or unsympathetic)" @Raychaudhuri2022.

# Features
The original survey data assessed participants on 45 variables, being representative of geographical location, education level, polictical affiliation, ideology, and racial attitudes and affiliations. The main sample consists of 1,517 White American adults from the NORC Amerispeak Panel, a national probability based sample. The other sample was from the survey firm Dynata. The original paper includes three data sets; data from pre-test (Dynata panel), data from main experiment (NORC Amerispeak Panel), and data for the state-level opioid mortality analysis (CDC). However, this reproduction is focused solely on the data from the main experiement and includes variables only found in the main experiment data set. This reproduction omits data for the state-level opioid mortality analysis (CDC) and the data from the pre-test (Dynata panel). This data sets were not relevant to the reproduction. This reproduction also changed the name of some of the main experiments variables in the data set for better clarity. The data set was then cleaned to include only relevant variables applicable to this reproduction. @tbl-cleaned_data shows a sample of the cleaned data set.

```{r}
#| warning: false
#| echo: false
#| label: tbl-cleaned_data
#| tbl-cap: Cleaned Data

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

head(analysis_data)

@@

# Reading in data
analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"), show_col_types = FALSE)

# Here I am selecting electing relevant columns from the dataset and reshaping the data from wide to long format
data_long <- analysis_data |>
  select(sympathetic_white, sympathetic_black, unsympathetic_white, unsympathetic_black, policy) |>
  pivot_longer(cols = -policy, names_to = "category", values_to = "value") |>
  filter(value == 1) |>
  group_by(category) |>
  summarise(support_for_treatment = mean(policy, na.rm = TRUE),
            support_for_arrest = 1 - support_for_treatment)

# Here I am further reshaping of the data for plotting
# I am also melting the data frame to have a single column for policy type and another for proportion
data_long_melted <- pivot_longer(data_long, cols = c(support_for_treatment, support_for_arrest),
                                 names_to = "policy_type", values_to = "proportion") |>
  mutate(policy_type = factor(policy_type, levels = c("support_for_treatment", "support_for_arrest")))

# Creating a bar graph using ggplot
ggplot(data_long_melted, aes(x = category, y = proportion, fill = policy_type)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = c("support_for_treatment" = "blue", "support_for_arrest" = "red")) +
  labs(title = "Policy Support by Valence and Race (Media Frames)",
       x = "Valence and Race",
       y = "Proportion",
       fill = "Policy Type") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

# Create the Forest Plot
ggplot(tidy_model, aes(x = estimate, y = term)) +
  geom_point() + # Add points for estimates
  geom_errorbarh(aes(xmin = estimate - std.error, xmax = estimate + std.error), height = 0.2) + # Error bars
  theme_minimal() + # Use a minimal theme
  labs(x = "Estimate", y = "Variable", title = "Ideology Model Estimates") + # Labels
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") # Vertical line at zero
```

@@

### Findings
The null hypothesis ($H_0$) stated that there would be no interaction effect between political ideology and media framing on support for opioid abuse treatment policy. However, @fig-interactions shows varying estimates across different combinations of political ideology and media framing. This suggests that there may be an interaction effect. This is because the estimates for both liberal and conservative ideologies when paired with certain sympathetic framings are positive and do not overlap with the zero line, indicating a significant effect. This suggests that there is indeed some interaction effect, which leads to the rejection of the null hypothesis.

@@

### Future Research 
Future research could look into the psychological mechanisms that may explain why and how political ideologies modulate responses to media framing of opioid users. It is also imperative to understand the role of individual identity, such as race and personal experience with opioid abuse, in shaping one's reaction to policy framing. Could it be that personal connections to the opioid crisis, either through community impact or personal acquaintance with sufferers, are powerful enough to override political predispositions? Personal experience could play a significant role in an individuals views on media framing and policy and seems like a strong future area of research regarding both this paper and the original.

# Conclusion 
This study contributes to the growing body of literature that seeks to understand the opioid crisis not just as a public health issue, but as a societal issue that is deeply intertwined with race, politics, ideology, and media. By replicating and extending the work of Raychaudhuri, Mendelberg, and McDonough, this paper sheds light on the ways in which these factors interact to shape policy preferences, offering insights that could inform more effective and equitable approaches to addressing the opioid epidemic.

\newpage
